### 2019-09-13 paper/HOLMultivariate.tex
Enriched Table 1 + TeX outputs of "In/Out"
Updated CCS references
Updated generated theories
Separate FV and BV definitions
Updated generated TeX

\newcommand{\HOLMultivariateDate}{04 Settembre 2019}
\newcommand{\HOLMultivariateTime}{13:47}

@@

       \HOLConst{context} \HOLBoundVar{Xs} \HOLSymConst{\ensuremath{=}}
       \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}.

@@

            \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Xs}\ensuremath{)}

@@

       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLSymConst{\ensuremath{=}}
       \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}.

@@

            \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Xs}\ensuremath{)}

@@

       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{p}\ensuremath{)}. \HOLConst{FV} \HOLBoundVar{p} \HOLConst{\HOLTokenSubset{}} \HOLTokenLeftbrace{}\HOLBoundVar{x}\HOLTokenRightbrace{}\ensuremath{)} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}

@@

       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}.
           \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \ensuremath{(}\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
           \ensuremath{(}\ensuremath{[}\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{P}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E\sp{\prime}}\ensuremath{)}

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{Xs}.
       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \ensuremath{(}\ensuremath{[}\HOLConst{MAP} \HOLConst{var} \HOLBoundVar{Xs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E}\ensuremath{)}

@@

       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}

@@

@@

       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}

@@

@@

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{x} \HOLBoundVar{xs} \HOLBoundVar{y} \HOLBoundVar{ys}.
       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{x} \HOLBoundVar{xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{xs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{ys}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \ensuremath{(}\HOLConst{fromList} \ensuremath{(}\HOLBoundVar{x}\HOLSymConst{::}\HOLBoundVar{xs}\ensuremath{)} \ensuremath{(}\HOLBoundVar{y}\HOLSymConst{::}\HOLBoundVar{ys}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{fromList} \HOLBoundVar{xs} \HOLBoundVar{ys} \HOLSymConst{|+} \ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}\ensuremath{)}\ensuremath{)}

@@

@@

>>>>

\newcommand{\HOLMultivariateDate}{13 Settembre 2019}
\newcommand{\HOLMultivariateTime}{10:02}

@@

       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}}

@@

       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Xs}

@@

       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenEquiv{}}

@@

       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Xs}

@@

       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{p}\ensuremath{)}. \HOLConst{FV} \HOLBoundVar{p} \HOLConst{\HOLTokenSubset{}} \HOLTokenLeftbrace{}\HOLBoundVar{x}\HOLTokenRightbrace{}\ensuremath{)} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}

@@

       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{E\sp{\prime}}. \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E\sp{\prime}}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\ensuremath{[}\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{P}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E\sp{\prime}}\ensuremath{)}

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{Xs}. \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\ensuremath{[}\HOLConst{MAP} \HOLConst{var} \HOLBoundVar{Xs}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E}\ensuremath{)}

@@

   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}. \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Y} \HOLBoundVar{E}. \HOLConst{context} \HOLBoundVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}
\begin{SaveVerbatim}{HOLMultivariateTheoremscontextXXrecYY}

@@

       \HOLConst{context} \HOLBoundVar{Xs} \HOLBoundVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{Y} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}

@@

\newcommand{\HOLMultivariateTheoremscontextXXrecYY}{\UseVerbatim{HOLMultivariateTheoremscontextXXrecYY}}

@@

\begin{SaveVerbatim}{HOLMultivariateTheoremsfromListXXDOMSUBXXNOTXXINXXDOM}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X} \HOLBoundVar{Xs} \HOLBoundVar{Ps}.
       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \ensuremath{(}\HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{\setminus}} \HOLBoundVar{X} \HOLSymConst{\ensuremath{=}} \HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps}\ensuremath{)}
\newcommand{\HOLMultivariateTheoremsfromListXXDOMSUBXXNOTXXINXXDOM}{\UseVerbatim{HOLMultivariateTheoremsfromListXXDOMSUBXXNOTXXINXXDOM}}

@@

       \HOLSymConst{\HOLTokenNeg{}}\HOLConst{MEM} \HOLBoundVar{X} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \ensuremath{(}\HOLConst{fromList} \ensuremath{(}\HOLBoundVar{X}\HOLSymConst{::}\HOLBoundVar{Xs}\ensuremath{)} \ensuremath{(}\HOLBoundVar{P}\HOLSymConst{::}\HOLBoundVar{Ps}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLSymConst{|+} \ensuremath{(}\HOLBoundVar{X}\HOLSymConst{,}\HOLBoundVar{P}\ensuremath{)}\ensuremath{)}

@@

\HOLThmTag{Multivariate}{context_rec'}\HOLMultivariateTheoremscontextXXrecYY

@@

\HOLThmTag{Multivariate}{fromList_DOMSUB_NOT_IN_DOM}\HOLMultivariateTheoremsfromListXXDOMSUBXXNOTXXINXXDOM
